Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-11-30 paper/paper.tex
the vertices of

Also, $p \lessmap{k} t$ implies that for each $q \in N(p) \setminus P_k$, where $P_k$
is some subset of $P$ with $\left| P_k \right| \leq k$, we have $q \lessmap{k} u$, where $u \in N(t)$ and
each $u$ is distinct.  Then $\deg(q) - k \leq \deg(u)$, by \cref{prop:deg}.  Hence $\nds(p)
\lesspreceq{k} \nds(t)$.
\end{proof}

>>>>

Also, $p \lessmap{k} t$ implies that for each $q \in N(p) \setminus P_k$, where $P_k$ is some subset
of the vertices of $P$ with $\left| P_k \right| \leq k$, we have $q \lessmap{k} u$, where $u \in
N(t)$ and each $u$ is distinct.  Then $\deg(q) - k \leq \deg(u)$, by \cref{prop:deg}.  Hence
$\nds(p) \lesspreceq{k} \nds(t)$.
\end{proof}
